### 2017-01-03 paper/evaluation.tex
removed unnecessary word
pass on text

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from Github. We are
interested in understanding the prevalence of long test runs, the main
sources of cost, and how do developers explore parallelism to improve
execution performance. More specifically, we pose the following
research questions:

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How often are parallelization features present in
build files?}
\newcommand{\RQC}{What is the impact of parallalelization?}

@@

We are interested to evaluate non-trivial test suites on popular
projects that are in activity. We used the Github's Search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the Github API considers the
predominant language as the primary language.}; (2) the project has at
least 100 stars; (3) latest update on (or after) January 1st, 2016;
(4) the \emph{readme} file contains the string \emph{mvn}.

On Github, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects: we assumed that Github users are likely to
demonstrate interest on well-tested projects. The third criteria is a
constraint to skip projects without recent activity. The fourth
criteria is an approximation to find projects with Maven support. We
used Maven as a reference due to its popularity on Java projects and
to automate our evaluation scripts. The rationale is that if the
string \emph{mvn} exists in the \emph{readme} file, it may represent a
Maven call (\eg, to compile or test the project).
Figure~\ref{fig:subject-query} illustrates the query as an HTTP
request.

@@

\end{lstlisting}
\caption{\label{fig:subject-query} Query to the Github API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

@@

To evaluate the presence of parallelization settings, we considered
the \numSubjsRqTwo{} subjects from the groups \emph{long} and
\emph{medium} identified in Section~\ref{sec:rqone}. We focused in
these two groups because they represent costly test suites and are
more likely that the developers may have used strategies to reduce the
execution cost (\eg, running parts of the tests in different threads).
We computed the frequence of the parallelism modes (see Section
\ref{sec:modes}) using a semi-automatic approach: we first discover
automatically the relevant configuration files and then we manually
inspect them to eliminate false-positves (\eg, commented
configuration).  Figure \Fix{N} describes the discovery step. We first
list the paths of all build file and then we filter only the build
files that contain any of the keywords, \CodeIn{forkMode},
\CodeIn{forkCount}, or \CodeIn{parallel}. Notice that, for Maven
projects, these any keywords exist in any possible parallelism
configuration \Fix{cite surefire doc}.

>>>>

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from \github{}. We are
interested in understanding the prevalence of long test runs, the main
sources of cost, and how do developers explore parallelism to improve
execution performance. More specifically, we pose the following
research questions:

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How often are parallelization features in
build files?}
\newcommand{\RQC}{What is the impact of parallalelization?}

@@

We are interested to evaluate non-trivial test suites on popular
projects that are in activity. We used the \github{}'s search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the \github{} API considers the
predominant language as the primary language.}; (2) the project has at
least 100 stars; (3) latest update on (or after) January 1st, 2016;
(4) the \emph{readme} file contains the string \emph{mvn}.

On \github{}, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects: we assumed that \github{} users are likely to
demonstrate interest on well-tested projects. The third criteria is a
constraint to skip projects without recent activity. The fourth
criteria is an approximation to find projects with Maven support. We
used Maven as a reference due to its popularity on Java projects and
to automate our evaluation scripts. The rationale is that if the
string \emph{mvn} exists in the \emph{readme} file, it may represent a
Maven call (\eg, to compile or test the project).
Figure~\ref{fig:subject-query} illustrates the query as an HTTP
request.

@@

\end{lstlisting}
    \caption{\label{fig:subject-query} Query to the \github{} API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

@@

To evaluate the presence of parallelization settings, we considered
the \numSubjsRqTwo{} subjects from the groups \emph{long} and
\emph{medium} identified in Section~\ref{sec:rqone}. We focused in
these two groups because they represent costly test suites and are
more likely that the developers may have used strategies to reduce the
execution cost (\eg, running parts of the tests in different threads).
We computed the frequence of the parallelism modes (see Section
\ref{sec:modes}) using a semi-automatic approach: we first discover
automatically the relevant configuration files and then we manually
inspect them to eliminate false-positves (\eg, commented
configuration).  Figure~\ref{fig:discovery-step} describes the
discovery step. We first list the paths of all build file and then we
filter only the build files that contain any of the keywords,
\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}. Notice
that, for Maven projects, these any keywords exist in any possible
parallelism configuration \Fix{cite surefire doc}.
